MINOS Handover Plots

### 2023-10-19 minos/validation/cross_validation_default.Rmd
Fixed dependency for CV runs and updated CV vis script with material deprivation composite visualisations
Addition of chron_disease to cross validation scripts, and small tweaks to both validation scripts

>>>>

# Material Deprivation

```{r}
matdep.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'matdep')

cv_ordinal_plots(pivoted.df = matdep.pivoted, 
                 var = 'matdep',
                 save = FALSE)
rm(matdep.pivoted)
```

# Chronic Disease

```{r}
chron_disease.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'chron_disease')

cv_ordinal_plots(pivoted.df = chron_disease.pivoted, 
                 var = 'chron_disease',
                 save = FALSE)
rm(chron_disease.pivoted)
```

### 2023-10-19 minos/validation/handovers.Rmd
Addition of chron_disease to cross validation scripts, and small tweaks to both validation scripts

sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)
# 
# spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
#                save = shall.we.save,
#                save.path = save.path)

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, matdep) %>%
#   filter(!matdep %in% miss.values)
# base.s <- base.dat %>%
#   select(pidp, age, time, matdep) %>%
#   filter(!matdep %in% miss.values)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'matdep',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

>>>>

sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)

spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, matdep) %>%
  filter(!matdep %in% miss.values)
base.s <- base.dat %>%
  select(pidp, age, time, matdep) %>%
  filter(!matdep %in% miss.values)

spaghetti_plot(spag, 'matdep',
               save = shall.we.save,
               save.path = save.path)
